Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-24 paper/paper.qmd
final paper updates

The AFINN index in @fig-sentiment-number portrays a similar trend. On a scale of -5 to 5, SOC literature from these five authors mostly carry a negative sentiment, observable in the significant difference in height between the negative trendlines and the positive trendlines. Eliot's works are the most negative with 37% of words being -2 on the emotional scale between -5 and 5. Respectively, Woolf's, Proust's and Joyce's tail beind at 33%, 32% and 31%, averaging out to be -2.2 on the emotional scale between -5 and 5. While a large percentage Mansfield's works are positive, 24% of her words-the largest percentage of hers-are negative, earning a -2.2 negative score between -5 and 5 in the AFINN index.

>>>>

The AFINN index in @fig-sentiment-number portrays a similar trend. On a scale of -5 to 5, SOC literature from these five authors mostly carry a negative sentiment, observable in the significant difference in height between the negative trendlines and the positive trendlines. Eliot's works are the most negative with 37% of words being -2 on the emotional scale between -5 and 5. Respectively, Woolf's, Proust's and Joyce's tail beind at 33%, 32% and 31%, averaging out to be -2.2 on the emotional scale between -5 and 5. While a great portion of Mansfield's works are positive, 24% of her words-her largest percentage-are negative, earning a -2.2 negative score between -5 and 5 in the AFINN index.
